### 2024-08-15 cognitive-bias.qmd
20240815 - clean up citations

@Miller2013c describes cognitive biases in fantasy sports.
Examples of cognitive biases relevant to fantasy football that result from one or more heuristics include:

@@

Consider another example adapted from @Miller2013c: two players scored the same number of points in a given week.
A Wide Receiver scored 1.6 points from 16 receiving yards on 1 target.
A Running Back scored 1.6 points from 56 receiving yards and two dropped fumbles.
The manager may harbor more blame for the player who performed a harmful action (losing two fumbles) than the player who received only one target (harmful inaction).

@@

*Endowment effect bias* is the tendency to overvalue merely because one owns it.
That is, a manager tends to value the same player more when they play for their team rather than an opponent's team.
When trading, the endowment effect bias might lead a manager to demand more to trade away a player than to acquire the same player [@@Miller2013c].
For instance, a manager might overvalue a player they drafted in the first round, refusing to trade them even if they could get a better-performing player in return.

>>>>

Miller [-@Miller2013c] describes cognitive biases in fantasy sports.
Examples of cognitive biases relevant to fantasy football that result from one or more heuristics include:

@@

Consider another example adapted from Miller [-@Miller2013c]: two players scored the same number of points in a given week.
A Wide Receiver scored 1.6 points from 16 receiving yards on 1 target.
A Running Back scored 1.6 points from 56 receiving yards and two dropped fumbles.
The manager may harbor more blame for the player who performed a harmful action (losing two fumbles) than the player who received only one target (harmful inaction).

@@

*Endowment effect bias* is the tendency to overvalue merely because one owns it.
That is, a manager tends to value the same player more when they play for their team rather than an opponent's team.
When trading, the endowment effect bias might lead a manager to demand more to trade away a player than to acquire the same player [@Miller2013c].
For instance, a manager might overvalue a player they drafted in the first round, refusing to trade them even if they could get a better-performing player in return.
